---
title: "Lab 7: Multiple linear regression intro"
author: "Thomas Lenihan"
date: "11/9/2021"
output: html_document
---

```{r setup, include=TRUE, message = FALSE, warnings = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warnings = FALSE)

library(tidyverse)
library(palmerpenguins)
library(GGally)
library(broom)
library(kableExtra)
library(modelsummary)
library(stargazer)
library(ggthemes)
```

## Explore penguins

Use `GGally::ggpairs()` to create a pairs plot.

```{r message = FALSE, warnings = FALSE}
ggpairs(penguins)
```

That's kind of overkill. Let's simplify the variables that we unclide in our ggpairs plot: 

- species
- bill_length_mm through body_mass_g

```{r message = FALSE, warnings = FALSE}
penguins %>% 
  select(species, bill_length_mm:body_mass_g) %>% 
  ggpairs(aes(color = species))
```

## Multiple linear regression 

We are going to try to understand a bit better the relationships between multiple predictor variables and an outcome which is penguin body mass. 

The different predictor variables we're going to try are: 

- species
- flipper length
- sex
- bill depth

### Model 1

Model body mass based on only flipper length and bill depth 
(bas idea... there are important variables missing, think sexual dimorphism)

```{r}
model_1 <- lm(body_mass_g ~ flipper_length_mm + bill_depth_mm, 
              data = penguins)
# call a model by name to return only the coefficients
model_1

summary(model_1)
```

#### Communicating the results of the model: 
Looking at the eqn of the line (coefficients): if everything else is held constant, for every 1 mm increase in flipper length, there is, on average, an expected 51.54 gram increase in body mass. 

Looking at the R^2: 76.1 percent of variance in penguin body mass is explained by the model (penguin flipper length and bill depth).

Actually -- we think that a model for penguin body mass should contain variables species, flipper length, and penguin sex.

```{r}
model_2 <- lm(body_mass_g ~ flipper_length_mm + species + sex, 
            data = penguins)
# checking out the coefficients
model_2

# Try interpreting the coefficients for:
  #flipper length, Gentoo, male


```

Interpretations: 

- flipper length: if everything else is held constant, there is an average 20.02 g increase in body mass for every 1 mm increase in flipper length.

- Gentoo: on average, a Gentoo penguin weighs 836 grams more than an Adelie penguin, if everything else remains constant.

-Male: On average, a male penguin will weigh an average 530.38 grams more than a female penguin, if everything else is held constant. On average.

## Visualize this model

```{r}
ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g))+
  geom_point(aes(color = species))+
  facet_wrap(~sex)+
  theme_minimal()
```

## A couple ways to get and report MLR model outcomes

Use broom::tidy() to get mode coefficient info in a tidy data frame. 

```{r}
penguin_model2_coef <- tidy(model_2)

penguin_model2_coef
```

try to write in-line code `r` that spits out the coefficient for Gentoo.

`r round(penguin_model2_coef[4,2],2)`

or `r penguin_model2_coef$estimate[4]`

## Look at model diagnostics

Use the plot() function 

```{r}
plot(model_2)

summary(model_2)
```

## Report the model outputs in a summary table

use modelsummary():

```{r}
modelsummary(model_2)
```

or use stargazer:

```{r, results = "asis}
stargazer(model_2, model_1, type = "html")
```


